\Title

### 2021-07-14 manuscript/content.tex
Revise discussion of source location and gradient boosting

\begin{figure}
    \includegraphics[width=\linewidth]{figs/eql-boost-airborne.pdf}
    \caption{
        Interpolation error for gradient-boosted equivalent sources using
        randomized (a) and sequential (b) window order.
        (a and b)~Pseudo-color maps of the differences between the target grid
        and the interpolated synthetic airborne survey data.
        (c)~Root-mean squared error after each iteration of the
        gradient-boosting algorithm.
}
\label{fig:eql-boost-airborne}
\end{figure}

@@

\begin{figure*}
    \includegraphics[width=\linewidth]{figs/australia-memory-cv-error.pdf}
    \caption{
        (a) Amount of computer memory needed to store the largest Jacobian
        matrix for different window sizes. Our implementation uses double
        precision floating point numbers (64 bits) for the Jacobian.
        (b) K-Fold cross-validation root-mean square errors obtained after the
        for each pair of damping and depth parameters. The orange
        square highlights the minimum.
        (c) Root-mean square error against the observed data after each
        iteration of the gradient-boosting algorithm.
    }
    \label{fig:australia-memory-cv-error}
\end{figure*}

@@

The results of our tests on synthetic data
(Figs.~\ref{fig:ground-survey-differences}
and~\ref{fig:airborne-survey-differences}) show that there are no significant
differences between source distribution strategies, both in terms of the
interpolation RMS errors and from visual inspection of the difference maps.
Therefore, we argue that all source distribution strategies are able to produce
comparably accurate interpolations.
Nevertheless, the \emph{block-averaged sources} strategy make use of fewer
sources when compared with other strategies, which reduces the computational
load of estimating the sources coefficients and forward modelling.
To ensure that the interpolation is able to reproduce the high frequencies in
the data, the block size used in the averaging should be chosen to match the
desired grid resolution.

@@

From Fig.~\ref{fig:gradient-boosted-comparison}a
and~\ref{fig:gradient-boosted-comparison}c, we can see that the
gradient-boosted equivalent sources produce slightly less accurate
interpolation results but are able to achieve smaller computation times than
regular equivalent sources.
The reduction of the accuracy might be due to the gradient boosting algorithm
failing to converge to the global minimum of the goal function.
As the windows increase in size, interpolation error decreases because more data
points are included into the least-squares fitting of the source coefficients.
At the same time, the fitting process becomes faster because of a reduction in
the number of iterations.
Our results indicate that it is desirable to maximize the window size up to the
point that the Jacobian matrices still fit within the available computer
memory.

@@

Finally, the results in Fig.~\ref{fig:eql-boost-airborne} highlight the
importance of randomizing the order in which the overlapping windows are
iterated.
Running the gradient boosting algorithm sequentially produces less accurate
predictions and decreases the convergence rate.

>>>>

\begin{figure}
    \includegraphics[width=\linewidth]{figs/eql-boost-airborne.pdf}
    \caption{
        Interpolation error for gradient-boosted equivalent sources using
        randomized (a) and sequential (b) window order.
        (a and b)~Pseudo-color maps of the differences between the target grid
        and the interpolated synthetic airborne survey data.
        The color scale has been cropped to the same range as
        Fig.~\ref{fig:airborne-survey-differences}.
        (c)~Root-mean squared error after each iteration of the
        gradient-boosting algorithm.
}
\label{fig:eql-boost-airborne}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=\linewidth]{figs/australia-memory-cv-error.pdf}
    \caption{
        (a) Amount of computer memory needed to store the largest Jacobian
        matrix for different window sizes. Our implementation uses double
        precision floating point numbers (64 bits) for the Jacobian.
        (b) Root-mean square error against the observed data after each
        iteration of the gradient-boosting algorithm.
        (c) K-Fold cross-validation root-mean square errors obtained for each
        pair of damping and depth parameters. The orange star highlights the
        minimum.
    }
    \label{fig:australia-memory-cv-error}
\end{figure}

@@

The results of our tests on synthetic data
(Figs.~\ref{fig:ground-survey-differences}
and~\ref{fig:airborne-survey-differences}) show that there are no significant
differences in interpolation accuracy between source distribution strategies,
both in terms of the interpolation RMS errors and from visual inspection of the
difference maps.
Therefore, we conclude that all source distribution strategies are able to
produce comparable interpolations.
Nevertheless, the \emph{block-averaged sources} strategy makes use of fewer
sources when compared with other strategies, which reduces the computational
load of estimating the sources coefficients and forward modelling.
To ensure that the interpolation is able to reproduce the high frequencies in
the data, the block size used in the averaging should be chosen to match the
desired grid resolution.

@@

From Fig.~\ref{fig:gradient-boosted-comparison}a
and~\ref{fig:gradient-boosted-comparison}c, we can see that the
gradient-boosted equivalent sources produce slightly less accurate
interpolation results but are able to achieve smaller computation times than
regular equivalent sources.
The reduction of the accuracy might be due to the gradient boosting algorithm
failing to converge to the global minimum of the goal function.
As the windows increase in size, interpolation error decreases because more data
points are included into the least-squares fitting of the source coefficients.
At the same time, the fitting process becomes faster because of a reduction in
the number of iterations.
Our results indicate that it is desirable to maximize the window size,
which can be done up to the point that the Jacobian matrices still fit within
the available computer memory.

@@

Finally, the results in Fig.~\ref{fig:eql-boost-airborne} highlight the
importance of randomizing the order in which the overlapping windows are
iterated.
Running the gradient boosting algorithm sequentially produces less accurate
predictions and decreases the convergence rate of the method.
